*DCVtestkit*: an R package for analysis of quality control dilution curves

### 2022-10-13 Manuscript/manuscript.qmd
Update the Summary to Federico's correction.

In a metabolomics and lipidomics workflow, a linear response in quality control dilution curves is used to assess the quality of molecules measured for further analysis. Current software tools only allow the analyst to repetitively plot, view and analyse the dilution curve one at a time which is a tedious and time-consuming process. In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$, which are insufficient to fully understand the shape of the dilution curves. `DCVtestkit` aims to provide additional summary statistics of dilution curves from various literatures which are not implemented in the current software tools. It also helps to reduce the analyst's workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file. In addition, it can also create an interactive trellis displayed as a HTML folder for analyst to do exploratory analysis on these dilution curve results.

>>>>

In metabolomic and lipidomic workflows, a linear response in dilution series generated from pooled quality control (QC) samples is used to assess the quality of the measurement of molecules measured before further analysis. Most of the currently used software only allow the analyst to repetitively plot, view and analyse the dilution curves one at a time, a tedious and time-consuming process. In addition, summary statistics of dilution curves are limited to the Pearson Correlation Coefficient $R$ and/or Coefficient Of Determination $R^2$, which are insufficient to fully understand the shape of the dilution curves. DCVtestkit aims to provide additional summary statistics for dilution curves, taken from previous publications but which are not implemented in the current software tools. It also helps to reduce the analyst’s workload by analysing many dilution curves automatically, reporting the statistical results in Excel and recording the dilution plots in a pdf file. In addition, it can also create an interactive trellis displayed as a HTML folder for more exploratory analyses.
